### 2021-06-10 paper/NIHGrant.tex
Add section on subject recruitment, start fiddling with reconstructing spectrograms

@@

Subjects will be recruited from the clinical population by \hl{our clinical collaborator}
and will be assessed by the Tinnitus Severity Scale.
We will not screen for unilateral or bilateral tinnitus but will only include subjects
with primary (\ie subjective, not somatosensory) tinnitus.

During the experiment, subjects will be asked to perform an computerized alternate forced-choice task,
selecting whether the presented stimulus sounds similar to their tinnitus percept or not.
They will be told that the stimuli are representations of tinnitus from other patients.
Each signal will be presented to subjects over headphones
at an audible level ($\approx 75$ dB SPL) after which
the subject will select either ``yes'' or ``no'' via keyboard presses.
The next trial will begin after a 500-ms pause.
Subjects will be asked to perform the task in hour-long blocks with a rest period in-between.
Subjects can perform the task for one or more blocks at their choice,
and will be compensated for their participation.

@@

We will implement a variational autoencoder (VAE), a type of unsupervised machine learning model
that learns a latent representation of data as well as how to generate new data
that appears similar to data the model has been presented with before.
A VAE consists of an encoder artificial neural network
which constructs a latent representation
as a zero-mean, unit-variance normal-distributed vector
and a decoder artificial neural network
that reconstructs the input (\autoref{fig:vae}).
By training the VAE on reconstructed representations,
forcing the encoder to create a latent representation
and the decoder to reproduce the input from the latent representation,
the model will learn the manifold of tinnitus percepts.
By sampling the latent vector,
we can generate new stimuli informed by the representations the model has learned.
One limitation of VAEs is that sampling from the latent vector
tends to produce new data points that appear noisy.
In our experiment, this is a benefit,
as noisy, random stimuli is crucial to reverse correlation.
Through this generative model,
we will create stimuli that appear closer to actual tinnitus percepts
by learning directly from the data
without introducing external experimenter bias.

>>>>

\paragraph{Subject Recruitment}

Subjects will be recruited from the clinical population by \hl{our clinical collaborator}
and will be assessed by the Tinnitus Severity Scale,
which measures the negative impact tinnitus has on a subject's quality of life.
We will not screen for unilateral or bilateral tinnitus but will only include subjects
with primary (\ie subjective, not somatosensory) tinnitus.

@@

During the experiment, subjects will be asked to perform an computerized alternate forced-choice task,
selecting whether the presented stimulus sounds similar to their tinnitus percept or not.
They will be told that the stimuli are tinnitus-like sounds corrupted by noise
and that not all will sound like their tinnitus percept.
Each signal will be presented to subjects over headphones
at an audible level ($\approx 75$ dB SPL) after which
the subject will select either ``yes'' or ``no'' via keyboard presses.
The next trial will begin after a 500-ms pause.
Subjects will be asked to perform the task in 80-trial blocks with a rest period in-between.
We will ask subjects to perform 20 blocks at minimum, which should take about a half an hour.
Subjects can perform the task for more blocks at their choice,
and will be compensated for their participation.

@@

We will implement a variational autoencoder (VAE), a type of unsupervised machine learning model
that learns a latent representation of data as well as how to generate new data
that appears similar to data the model has been presented with before.
A VAE consists of an encoder artificial neural network
which constructs a latent representation
as a zero-mean, unit-variance normal-distributed vector
and a decoder artificial neural network
that reconstructs the input (\autoref{fig:vae}).
By training the VAE on reconstructed representations,
forcing the encoder to create a latent representation
and the decoder to reproduce the input from the latent representation,
the model will learn the manifold of tinnitus percepts.
By sampling the latent vector,
we can generate new stimuli informed by the representations the model has learned.
One limitation of VAEs is that sampling from the latent distribution
tends to produce new data points that appear noisy.
In our experiment, this is a benefit,
as noisy, random stimuli is crucial to reverse correlation.
Through this generative model,
we will create stimuli that appear closer to actual tinnitus percepts
by learning directly from the data
without introducing external experimenter bias.
